Portable Development Methodology

### 2024-02-05 latex/ms.tex
.

\documentclass[journal]{IEEEtran}
\usepackage[boxed]{algorithm2e}
\usepackage[nopdftrailerid=true]{pdfprivacy}

@@

\begin{abstract}
	This paper proposes a portable development methodology.
	We release open source repositories of the examples use cases of this.
\end{abstract}

\section{Introduction}
Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough thus multiple versions of it exist in software development.
This non-portability of software development practices is a lost potential in reducing software development time.

In this paper we present the design and implementation of the Makefile for python and tex for document generation and then the Makefile for website creation.

\section{Make}
Make has existed for decades and has passed the test of time, while the container technology was standardized with the Open Container Initiative and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.

@@

@@

\section{Workflow}

\begin{algorithm}
	\KwData{User requirement}
	\If{user requirement is unimportant}{
		\Return{}
	}
	\If{it can be solved without software}{
		\Return{}
	}
	\If{a package already exists}{
		Introduce the package as a dependency in the relevant main.py\;
		\Return{}
	}
	\If{a relevant repository exists}{
		Make repository compatible with stack/method\;
		\Return{}
	}
	\If{it can be programmed within a relevant main.py}{
		Program it in a relevant main.py\;
		\Return{}
	}
	\If{it can be programmed as a dependency/dependent of another directory}{
		Create a new dependent directory\;
		\Return{}
	}
	Create a new repository\;
	\Return{}
	\caption{Workflow}
\end{algorithm}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage[boxed]{algorithm2e}
\usepackage[nopdftrailerid=true]{pdfprivacy}
\usepackage{hyperref}

@@

\begin{abstract}
	This paper proposes a portable development methodology.
	Repository example use cases are also presented.
\end{abstract}

\section{Introduction}
Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough thus multiple versions of each of them exist in software development.
Loosely defined practices introduce non-portability issues through time and space, increasing development costs.

In this paper we present a portable development methodology which is concrete enough to be portable and abstract enough to be of general use.
We also present example use cases for python and tex document generation and website creation.

\section{Make}
Make~\cite{fowler1990case} has been used since 1970s and some of its basic features were standardized by POSIX\@.
Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.

@@

\section{Containers}
Containers were standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.

@@

\section{Workflows}

\begin{algorithm}
	\KwData{New user requirement}
	\If{user requirement is unimportant}{
		\Return{}
	}
	\If{it can be solved without software}{
		\Return{}
	}
	\If{a package already exists}{
		Introduce the package as a dependency in the relevant main.py\;
		\Return{}
	}
	\If{a relevant repository exists}{
		Make repository compatible with stack/method\;
		\Return{}
	}
	\If{it can be programmed within a relevant main.py}{
		Program it in a relevant main.py\;
		\Return{}
	}
	\If{it can be programmed as a dependency/dependent of another directory}{
		Create a new dependent directory\;
		\Return{}
	}
	Create a new repository\;
	\Return{}
	\caption{Workflow for new user requirement}
\end{algorithm}
